%-------------------------
% Resume in Latex
% Author : Anshu Kumar
% Based off of: https://github.com/jakeryang/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
% only for pdflatex
% \input{glyphtounicode}

% fontawesome
\usepackage{fontawesome5}

% fixed width
\usepackage[scale=0.90,lf]{FiraMono}

% light-grey
\definecolor{light-grey}{gray}{0.83}
\definecolor{dark-grey}{gray}{0.3}
\definecolor{text-grey}{gray}{.08}

\DeclareRobustCommand{\ebseries}{\fontseries{eb}\selectfont}
\DeclareTextFontCommand{\texteb}{\ebseries}

% custom underline
\usepackage{contour}
\usepackage[normalem]{ulem}
\renewcommand{\ULdepth}{1.8pt}
\contourlength{0.8pt}
\newcommand{\myuline}[1]{%
  \uline{\phantom{#1}}%
  \llap{\contour{white}{#1}}%
}


% custom font: helvetica-style
\usepackage{tgheros}
\renewcommand*\familydefault{\sfdefault} 
%% Only if the base font of the document is to be sans serif
\usepackage[T1]{fontenc}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{0in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting - serif
% \titleformat{\section}{
%   \vspace{2pt} \scshape \raggedright\large % header section
% }{}{0em}{}[\color{black} \titlerule \vspace{-5pt}]

% TODO EBSERIES
% sans serif sections
\titleformat {\section}{
    \bfseries \vspace{2pt} \raggedright \large % header section
}{}{0em}{}[\color{light-grey} {\titlerule[2pt]} \vspace{-4pt}]

% only for pdflatex
% Ensure that generate pdf is machine readable/ATS parsable
% \pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-1pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & {\color{dark-grey}\small #2}\vspace{1pt}\\ % top row of resume entry
      \textit{#3} & {\color{dark-grey} \small #4}\\ % second row of resume entry
    \end{tabular*}\vspace{-4pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
      #1 & {\color{dark-grey}} \\
    \end{tabular*}\vspace{-4pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

% CHANGED default leftmargin  0.15 in
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{0pt}}

\color{text-grey}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge Anshu Kumar} \\ \vspace{5pt}
    \small \faPhone* \texttt{9341104340} \hspace{1pt} $|$
    \hspace{1pt} \faEnvelope \hspace{2pt} \texttt{kanshukumar0203@gmail.com} \hspace{1pt} $|$ 
    \hspace{1pt} \faGithub \hspace{2pt} {\href{https://github.com/Anshukumar26}{\myuline {GitHub}}} \hspace{1pt} $|$
    \hspace{1pt} \faBehance \hspace{2pt} {\href{https://www.behance.net/Behance}{\myuline {Behance}}} \hspace{1pt} $|$
    \hspace{1pt} \faLinkedin \hspace{2pt} {\href{https://www.linkedin.com/in/anshu-kumar-5337bb286/}{\myuline {LinkedIn}}} \\ \vspace{5pt} $|$
    \hspace{1pt} \faMapMarker* \hspace{2pt}\texttt{Ranchi, Jharkhand}
    \\ \vspace{-3pt}
\end{center}
%-----------SUMMARY-----------
\section{SUMMARY}

UI/UX Designer and Computer Science undergraduate with internship experience designing scalable web and mobile applications for EdTech products. Skilled in Figma, Design Systems, Wireframing, Prototyping, Responsive Design, User Flows, Information Architecture, Flutter, and Firebase. Passionate about creating accessible, user-centered digital experiences and collaborating with cross-functional teams to deliver production-ready interfaces.

%-----------PROGRAMMING SKILLS-----------
\vspace{-8pt}
\section{SKILLS}
 \begin{itemize}[leftmargin=0in, label={}]
    \small{\item{
    \textbf{UI/UX} {:  User Research, Wireframing, Prototyping, User Flow, Design Systems, Auto Layout, Components, Responsive Design, Dashboard Design}\vspace{2pt} \\
     \textbf{Development} {:  Flutter, Dart}\vspace{2pt} \\
     \textbf{Tools}     {:  Figma, FigJam, Canva, Adobe Photoshop, Git, GitHub}
    }}
 \end{itemize}


%-----------EXPERIENCE-----------
\vspace{-20pt}
\section{EXPERIENCE}
\resumeSubHeadingListStart

\resumeSubheading
{One Aim IT Solutions}{Feb. 2026 -- May 2026}
{UI/UX Design Intern}{Remote}


\resumeItemListStart
    \resumeItem{Designed 120+ high-fidelity UI screens across web dashboards, admin portals, and mobile applications using Figma.}
    \resumeItem{Built reusable design systems with Auto Layout, Components, and Variants to maintain consistency across products.}
    \resumeItem{Created user flows, wireframes, interactive prototypes, and responsive layouts for production-ready interfaces.}
    \resumeItem{Collaborated with developers to ensure pixel-perfect implementation and efficient developer handoff while improving usability and navigation.}
\resumeItemListEnd

\resumeSubHeadingListEnd


%-----------PROJECTS-----------
\vspace{-20pt}
\section{PROJECTS}
\resumeSubHeadingListStart

\resumeSubheading
{Academy One – EdTech Platform}
{}
{Figma, UI/UX}
{\href{}{\myuline {}}}

\resumeItemListStart
    \resumeItem{Designed Student, Admin, and Super Admin portals comprising 150+ responsive UI screens.}
    \resumeItem{Created scalable design systems including typography, color tokens, reusable components, and responsive layouts.}
    \resumeItem{Designed Course Management, Banner Management, Dashboard Analytics, User Management, and Content Management modules while optimizing navigation and user experience.}
\resumeItemListEnd
\vspace{-2pt}
\resumeSubheading
{E-Commerce Shopping App Using Flutter}
{}
{Flutter, Firebase}
{\href{https://github.com/Anshukumar26/shopping_app}{\myuline {GitHub Link}}}

\resumeItemListStart
    \resumeItem{Developed a Flutter e-commerce application integrated with Firebase Authentication and Cloud Firestore.}
    \resumeItem{Implemented secure authentication, shopping cart, wishlist, responsive product pages, and clean state management.}
    
\resumeItemListEnd
\vspace{-2pt}
\resumeSubheading
{PhonePe Redesign}
{}
{Figma, UI/UX Design}
{\href{https://www.figma.com/proto/77gpKuIXJ7P1LwCsvRQ992/Untitled?node-id=94-2\&t=gxSoHOVMoqNUusfi-1\&scaling=scale-down-width\&content-scaling=fixed\&page-id=0:1}{\myuline {Case Study}}}

\resumeItemListStart
    \resumeItem{Redesigned the payment experience using UX principles, improving navigation, accessibility, and visual hierarchy through high-fidelity prototypes.}
    
\resumeItemListEnd

%\resumeSubheading
%{MetaDoc Healthcare Website Redesign}

%{Figma, Web UI/UX}
%{\href{https://shorturl.at/qk3dZ}{\myuline {Case Study}}}

%\resumeItemListStart
%    \resumeItem{Designed a modern healthcare website interface with improved user experience}
%    \resumeItem{Created responsive layouts, design systems, and intuitive navigation}
%    \resumeItem{Focused on clean visual hierarchy and healthcare-oriented accessibility}
%\resumeItemListEnd



\resumeSubHeadingListEnd


%-----------EDUCATION-----------
\vspace{-20pt}
\section {EDUCATION}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Engineering and Management, Jaipur}{Graduating May 2027}
      {Bachelor of Technology (B.Tech) in Computer Science Engineering}{CGPA: 7.45/10}
      	
  \resumeSubHeadingListEnd


%-----------Certification-----------
\section {CERTIFICATION}
  \resumeSubHeadingListStart
       \resumeSubheading{UI/UX Design Internship | One Aim IT Solutions}{\hfill \href{https://drive.google.com/file/d/10raLvw66c79jmtnyjenxfCpUPdrU4qFD/view?usp=sharing}{\small\myuline{Internship Certificate}}{}{}}
    
      	
  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
